formula1

### 2020-02-20 inst/formula1.Rmd
actually show the evaluate

```{r,maxp2017}
mL2017 <- maxp(L2017)
dotchart(mL2017,pch=16,main='2017 Formula 1')
dotchart(log(mL2017)[1:23],pch=16,main='2017 Formula 1, log scale')
```

>>>>

```{r,maxp2017}
mL2017 <- maxp(L2017)
mL2017
dotchart(mL2017,pch=16,main='2017 Formula 1')
dotchart(log(mL2017)[1:23],pch=16,main='2017 Formula 1, log scale')
```
